---
title: "Homework 1"
author: "Elisabeth R Silver"
date: "02/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(dplyr,ggplot2,psych,stats,ggpubr)

```

## Chatterjee-Price employee attitude dataset

In this dataset, each row is the proportion of favorable responses from a sample of employees (_n_ = 35) at 30 companies for each column dimension (total _N_ = `r 35*30`). 

```{r load_data}
data(attitude)
```

### Satisfaction with raises

The average (standard deviation) percent of employees satisfied with their employer's raises is `r round(mean(attitude$raises), 2)`% (`r round(sd(attitude$raises), 2)`%). 

Visually, satisfaction with raises is roughly normally distributed, and there do not seem to be any outliers or egregious skew. The histogram has a roughly normal distribution, there are not any outlying points on the boxplot, and the points on the QQ plot mostly align with the QQ line, suggesting normality.


```{r plots_1}
#Create the histogram
hist(attitude$raises, main = 'Histogram of percent of employees satisfied with raises',
     xlab = "Percent satisfied")
#Create the boxplot
ggboxplot(attitude$raises, ylab="Percent satisfied", 
          xlab = "",
          title = "Percent of employees satisfied with raises")+ rremove("x.ticks") + rremove("x.text")
#Create the QQPlot
qqnorm(attitude$raises, pch = 1, frame = FALSE)
qqline(attitude$raises, col = "steelblue", lwd = 2)

```

Statistically, the skew and excess kurtosis are not particularly large:

```{r describe_data_1}
#More descriptives
psych::describe(attitude$raises)
```

Given the approximately normal distribution of this variable, I do not think that the distribution would affect subsequent analyses.

### Satisfaction with handling of employee complaints

The average (standard deviation) percent of employees satisfied with their employer's handling of employee complaints is `r round(mean(attitude$complaints), 2)`% (`r round(sd(attitude$complaints), 2)`%). 

Visually, satisfaction with handling of employee compaints is roughly normally distributed, and there do not seem to be any outliers or egregious skew. The histogram has a roughly normal distribution (although there is a slight negative skew), there are not any outlying points on the boxplot, and the points on the QQ plot mostly align with the QQ line:


```{r plots_2}
#Create the histogram
hist(attitude$complaints, 
     main = 'Histogram of percent of employees satisfied with\nhandling of complaints',
     xlab = "Percent satisfied")

#Create the boxplot
ggboxplot(attitude$complaints, ylab="Percent satisfied", 
          xlab = " ", title = "Percent of employees satisfied with\nhandling of complaints") + rremove("x.ticks") + rremove("x.text")
#Create the QQPlot
qqnorm(attitude$complaints, pch = 1, frame = FALSE)
qqline(attitude$complaints, col = "steelblue", lwd = 2)

```

Statistically, the skew and excess kurtosis are not particularly large (although the skew is negative, as the above graphs suggest):

```{r describe_data_2}
#More descriptives
psych::describe(attitude$complaints)
```

Given the approximately normal distribution of this variable, I do not think that the distribution would affect subsequent analyses. There aren't any outliers that would require some sort of treatment. 
